\part{Matem\'aticas}

\chapter{Ecuaciones diferenciales}
En est\'e cap\'itulo vamos a entender que es una ecuaci\'on diferencial. 

Para comenzar a formular lo que es una ecuaci\'on diferencial, comencemos explorando lo que es la en s\'i, la palabra ecuaci\'on, de donde proviene, ?`C\'omo hemos trascendido los seres humanos en el pensamiento de las ecuaciones? ?`Para que sirven las ecuaciones y por ende donde aplicarlas? Es un tarea muy dura, pero lo vamos a lograr, formulando  preguntas para ir llegando a respuestas y de estas respuestas dar el salto a lo que yo llamo familiarizaci\'on intelectual. 

?`Por qu\'e planteamos ecuaciones? tratemos de acercarnos a esta pregunta observando la siguiente ecuaci\'on
\begin{equation}\label{equ1.1}
	y+5 = 0
\end{equation}

?`Qu\'e elementos involucrados conocemos en la ecuaci\'on \ref{equ1.1}?

Los n\'umeros 5 y 0, son dos enteros y la variable $y$ representando lo desconocido en la ecuaci\'on, es decir, lo que queremos encontrar, si nos enfocamos en ese sentido, llegaremos a que $y=-5$. 
\begin{equation}
	y(x)=y^{\prime}(x)
\end{equation}
Note que tenemos una igualdad de funciones, una ecuaci\'on que se cumple solo para las funciones que son soluciones de la misma. ?`Cuales son estas funciones? las funciones $c\exp(x)$, de esta manera podemos definir este tipo de ecuaciones, ?`Por qu\'e es importante las ecuaciones diferenciales? ?`Qu\'e fen\'omenos describe el c\'alculo? en intervengan, la distancia, velocidades y aceleraciones.

\begin{definicion}[Ecuaci\'on diferencial]
Una ecuaci\'on diferencial es cualquier ecuaci\'on que contiene las derivadas de una o m\'as variables dependientes con respecto a una o m\'as variables independientes.
\end{definicion}
\begin{ejemplo}
	\begin{align}
		\frac{dy}{dx} + \frac{dz}{dx} &= 2y + z, \\
		\frac{\partial^{2}u}{\partial{x^{2}}} &= \frac{\partial^{2}u}{\partial t^{2}} - 2\frac{\partial u}{\partial t} 
	\end{align}
\end{ejemplo}


\part{Ingles}

\chapter{ Unknown words }
\begin{description}
	\item[Which: ]  cual ; pronombre: que.
	\item[Shall: ]  debera.
	\item [use:  ]  usar.
	\item[brief: ]  breve.
	\item[either:]	conjuci\'on : o, adjetive: Cualquiera de los dos, uno u otro; Adverbio: tambi\'en.
	\item[these: ] estos, estas.

\end{description}

\chapter{Ingl\'es A1}

Marco Com\'un Europeo de Referencia para las Lenguas (MCER): 

\section{An\'alisis de habilidades}

A continuaci\'on, encontramos un an\'alisis de los diferentes componentes del idioma y las habilidades individuales que un estudiante deber\'ia tener para recibir un certificado A1 de ingles: 

{\bf Compresi\'on auditiva}

Los estudiantes de nivel A1 deberi\'an ser capaces de entender un ingl\'es est\'andar simple, siempre y cuando sea hablado con claridad por alguien paciente y dispuesto ayudar. Especificamente, deberi\'an poder reconocer frases y palabras comunes, relacionadas con ellos mismos, su entorno y aquellos cercanos a ellos. Adem\'as, deber\'ian entender cosas como los n\'umeros, direcciones y otras instrucciones muy b\'asicas en ingl\'es.

Welcome everyone to the basic English course. A one for beginners. I'm your teacher, kira Sage, nice to meet you. Who am i? I am from the U.S.A I have taught C level executives and software engineers at companies like google skhynix, Tesla, Sony and more. I have nine years of teaching experience in countries like Usa and Japan. Here are a couple of interesting facts about me. I have visited four of the six Disneyland's around the world. This is me at Star Wars, Galaxy edge in Anaheim California. Also i have Master's degree in teaching T. Saw that means I can teach teachers and learners like you in this course you will learn the alphabet ah and un sentences with it's plural forms, sentences with there are numbers, colors, subject pronouns, professions, greetings, negative and interrogative statements, possessive adjectives. Days of the week, your hobbies, questions with what's your and to review everything from this course we'll have to wrap up class. Here's you'll learn all of the course concepts through worksheets, find the worsheets in the resources section through interactive quizzes and through interactive explanations on an imaginary website called plattso plattso is where we practice english so we can make friends online. Are you ready for this  fun adventure? I'll see you in the next class.


Bienvenido todos al curso the Ingles b\'asico. A1 para comenzar 



\begin{verbatim}
Intento 1: 
Welcome everyone to the Black Sea English course A1 for beginners I
 am here t-shirt carousel nice to me you Hoang I who on my I'm from
 the USA I have to see level executive a software engineer and companies
 like Google sky and Tesla Sony and more I cannae jeers of teaching experience in countries like USA and Japan he are Kobe of interesting
 facts about me I had visits of the seeds Disneyland around the world this is me at Star Wars Galaxy Edge in Anaheim California also I have
 massive degree in teaching t so that means can teach t-shirts in Learners like you in this course you will learn the alphabet I'm on
 sentence with it's pure Air Force sentence with there are numbers caller surgeon pronounce profession where teens interrogative
 status. Osiria Jetties days of the weave your hobbies question with what you ain't to review everything from this course we wait
 we all have to grab a glass of the course Concepts world war ships find a wall sheets in the results section throw in charity
 crisis and throw into righteous play Nations oh imagine a website called black English so we can make friends only are you
 ready for this funeral bencher Adventure I also see you in the next class.
         
         
 Segundo intento: 
 welcome everyone to the basic English course. a wife for beginners at
  Food dock. Avon for beginners sorry please thought a blunt for 
  beginners. A1 for beginners. I am your teacher call Ma Kira say Asahi 
  call Mama, nice to meet you. who I who am I. I am from the USA. I 
  hopped out I have towels. IHOP takeout see Liberty Security in Sulphur 
  and genius and companies like Google Skynet call mistakes Le gamma 
  Sony a moor Anne Moore Anne Moore Sony and more. I have 9 years of 
  teaching experience in countries like USA in Japan. Cher here. T R A 
  Copley. here are a couple off interesting facts about me. I had visit 
  visit. I had visited full of the sea Disneyland around the world. this 
  is me and it's sad worse, Galaxy Edge in Anaheim California. also I 
  have. also I had Mercer metzer Meister Meister mustard master. also I 
  heart muscle is degree and teach t. all soup IHOP Massillon he's they 
  greet and teach tea. soda means I can teach t-shirts in layers
\end{verbatim} 

\url{https://www.youtube.com/watch?v=EVNhOAEW784}

\url{https://howjsay.com/how-to-pronounce-taught}
Para pronuciar Taught comience colocando su lengua detr\'as de sus dientes superiores y agregue el sonidoo AH corto y abierto termine con una T colocando su lengua detr\'as de sus dientes superiores



Numbers class Two: 

Welcome to the 1st Module. This english fundamentals in this module.
In this Module you will learn the 
\begin{enumerate}
	\item alphabet.
	\item A and N 
	\item sentences with it's plural forms
	\item  and sentences with there are
\end{enumerate}
 this is the alphabet. Now let's go and learn on platzo.
 
 Welcome to plattzo. Now loading oh do you know what this is?
 
 it's capture. We need letters to unlock the capture. Well let's learn in this class. 
 
 You will learn the letters of the english alphabet. In the English Alphabet there are 26 letters. Let's practice. I will say a letter an repeat after me. Ready, let's go. A B Bravo. C D E. Excellent F G. Googd job H I J K, keep it up. L M magnificent N. Nice work. O P perfect Q R S super T terrific. U V very goog W wonderful X. Why Z in some countries this letter is zed.
 
 Now, you know the letters of the alphabet? A B C D E F G H I J K L M N O P Q R S T u v w x, y z. OR ZED. 	Let's use these letters to unlock the capture on plattzo.
 
 The capture says a phrase, not a robot. Let's spell the phrase letter by letter N O T A R O B O T. You did it. You unlock the capture. 
 
 Great job. it's your turn. Here is the alphabet but some letters are missing. 
 
 Type, the missing letters in the discussion panel. 
 Don't forget to download your worksheet from the resources section that worksheet is your plattzo profile. Complete the user name area of your plattzo profile on your woorksheet, keep this worksheet with you at all times. We will complete your plattzo profile in each module of this course. So keep ir ready for extra practice. Type your user name in the discussion panel.
 
 My user name is Kira K I R A. I'll see you in the next class.
 
 
 Email: jcausilmartinez@gmail.com
 
 Number phone: 314 796 81 19.
 
 User name: Javier Andres Causil Martínez


My introducction in is Spanish:  

Hola mi nombre es Javier Andr\'es Causil Mart\'inez, soy de Colombia del departamento de Antioquia en la ciudad de Caucasia. Tengo 27 a\~nos, soy Matem\'atico  de la Universidad de Antioquia y programador, me gusta la m\'usica, hacer deporte, aprender cosas nuevas. Siento gran pasi\'on por la m\'usica cl\'asica. 





